Fig 2

### 2020-08-24 analysis/figure-2.Rmd
now with htr2c for hyp

g <- plotcandidatechar(hypvsdf, "AVP") + labs(subtitle = "Hypothalamus")
h <- plotcandidatechar(hypvsdm, "AVP") + labs(y = NULL, x = "") + labs(subtitle = " ")
i <- plotremoval(hypvsdf, "AVP")+ labs(y = NULL) + labs(subtitle = " ")
j <- plotremoval(hypvsdm, "AVP") + labs(y = NULL, x = "")+ labs(subtitle = " ")
k <- plotreplacement(hypvsdf, "AVP") + labs(y = NULL)+ labs(subtitle = " ")
l <- plotreplacement(hypvsdm, "AVP") + labs(y = NULL, x = "")+ labs(subtitle = " ")

@@

#h <- boxplotextint(hypvsdf, "HTR2C", " ")

>>>>

g <- plotcandidatechar(hypvsdf, "HTR2C") + labs(subtitle = "Hypothalamus")
h <- plotcandidatechar(hypvsdm, "HTR2C") + labs(y = NULL, x = "") + labs(subtitle = " ")
i <- plotremoval(hypvsdf, "HTR2C")+ labs(y = NULL) + labs(subtitle = " ")
j <- plotremoval(hypvsdm, "HTR2C") + labs(y = NULL, x = "")+ labs(subtitle = " ")
k <- plotreplacement(hypvsdf, "HTR2C") + labs(y = NULL)+ labs(subtitle = " ")
l <- plotreplacement(hypvsdm, "HTR2C") + labs(y = NULL, x = "")+ labs(subtitle = " ")

@@
